### 2021-04-23 input/conclusion.tex
highligh properties

With the advent of the edge and IoT era, major distributed services
proposed by our community should be revised in order to mitigate as
much as possible trafic between \processes.  In this paper, we tackled
the problem of content indexing, a key service for storage systems.
\TODO{pas vraiment du content indexing}
%
Our proposal relies on a logical partitioning of the infrastructure
that is maintained according to replicas creations/removals and
infrastructure changes. Through an efficient scoped broadcast, each
\process composing the infrastructure knows eventually where the best
replica for a particular content is. The major difficulty is to handle
concurrent operations, each having a different scope and ensure the
correct convergence of the system.
%
We proposed an implementation of this protocol called \NAME and
evaluated it on top of Peersim. The simulations confirmed the
correctness of our protocol as well as the confinement of the traffic
only where it is needed.

>>>>

With the advent of the edge and IoT era, major distributed services
proposed by our community should be revised in order to mitigate as
much as possible trafic between \processes.  In this paper, we tackled
the problem of content indexing, a key service for storage systems.
\TODO{pas vraiment du content indexing}
%
More precisely, we proposed to address it as a dynamic logical partitioning of the infrastructure
that should be maintained according to replicas creations/removals and
infrastructure changes. Through an efficient scoped broadcast, each
\process composing the infrastructure knows eventually where the best
replica for a particular content is. The major difficulty is to handle
concurrent operations, each having a different scope and ensure the
correct convergence of the system. We defined multiple properties that highlight this complexity.

We proposed an implementation of this protocol called \NAME and
evaluated it on top of Peersim. The simulations confirmed the
correctness of our protocol as well as the confinement of the traffic
only where it is needed.
